MHF SCP Experiment Visualisations

### 2024-09-03 minos/outcomes/MHF_SCP_visualisations.Rmd
Added code to each plotting function to save each plot as a png file

  print(p1)
  print(p2)
}

@@

  print(p1)
  print(p2)
}
```

@@

  print(p1)
  print(p2)
}

@@

  print(p1)
  print(p2)
}

@@

  print(p1)
  #print(p2)
}
```

@@

  print(p1)
  #print(p2)
}
```

@@

  print(p1)
  print(p2)
}

@@

  print(p1)
  print(p2)
}
```

>>>>

  print(p1)
  print(p2)

  ggsave(filename = paste('SF_12', summary_type, deparse(substitute(scen_list)), '.png', sep = '_'),
         plot <- p1,
         path = 'plots')

  ggsave(filename = paste('SF_12_cost_ratio', summary_type, deparse(substitute(scen_list)), '.png', sep = '_'),
         plot <- p2,
         path = 'plots')
}

@@

  #print(p1)
  print(p2)

  ggsave(filename = paste('SF_12_cost_ratio_cumulative', summary_type, deparse(substitute(scen_list)), '.png', sep = '_'),
         plot <- p2,
         path = 'plots')
}
```

@@

  print(p1)
  #print(p2)

  ggsave(filename = paste('abs_rel_comparison', comparison_scen, '.png', sep = '_'),
         plot <- p1,
         path = 'plots')
}

@@

  print(p1)
  #print(p2)

  ggsave(filename = paste('abs_rel_comparison_init', comparison_scen, '.png', sep = '_'),
         plot <- p1,
         path = 'plots')
}

@@

  print(p1)
  #print(p2)

  ggsave(filename = paste('gender_comparison', comparison_scen, '.png', sep = '_'),
         plot <- p1,
         path = 'plots')
}
```

@@

  print(p1)
  #print(p2)

  ggsave(filename = paste('lone_parent_comparison', comparison_scen, '.png', sep = '_'),
         plot <- p1,
         path = 'plots')
}
```

@@

  print(p1)
  print(p2)

  ggsave(filename = paste('men_illness_risk_counts', summary_group, deparse(substitute(scen_list)), '.png', sep = '_'),
         plot <- p1,
         path = 'plots')

  ggsave(filename = paste('men_illness_risk_prop', summary_group, deparse(substitute(scen_list)), '.png', sep = '_'),
         plot <- p2,
         path = 'plots')
}

@@

  print(p1)
  print(p2)

    ggsave(filename = paste('men_illness_risk_counts_sensitivity', summary_group, deparse(substitute(scen_list)), '.png', sep = '_'),
         plot <- p1,
         path = 'plots')

  ggsave(filename = paste('men_illness_risk_prop_sensitivity', summary_group, deparse(substitute(scen_list)), '.png', sep = '_'),
         plot <- p2,
         path = 'plots')
}
```
